Bare Demo of IEEEtran.cls\\ for IEEE Conferences

### 2016-11-23 bare_conf.tex
New abstract needed

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Michael Shell}
\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
Georgia Institute of Technology\\
Atlanta, Georgia 30332--0250\\
Email: http://www.michaelshell.org/contact.html}
\and
\IEEEauthorblockN{Homer Simpson}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: homer@thesimpsons.com}
\and
\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
\IEEEauthorblockA{Starfleet Academy\\
San Francisco, California 96678--2391\\
Telephone: (800) 555--1212\\
Fax: (888) 555--1212}}

@@

% make the title area 
\maketitle
\begin{abstract} This work is focused on the prediction of affective
states using non-obtrusive sensors. Non-obtrusive sensors are preferred in this
work because of a hypothesis that states that an obtrusive sensor would alter
the affective states of a user. Specifically, the method uses data gathered from
a keyboard and mouse dynamics plugin embedded in a tutoring system designed for
the teaching of computer programming in the Python language. The tutoring system
requires from the user to practice their programming skills in order to progress
through the course, and the user’s creativity plays an important role in the
solving of programming exercises. Also a pre-processing method is applied, which
generates feature vectors consisting of 39 features representing each
interaction of the users by recording their keyboard and mouse dynamics. 149
feature vectors were generated and used as input of four different
classification algorithms: Naïve Bayes, J-48, k-NN, and Artificial Neural
Networks. These classification models are then compared by their performances
when classifying learners into five different affective states: boredom,
frustration, distraction, relaxation and engagement. Each of the classification
models achieved an accuracy of around 75\% and kappa of around 0.45, and, in
average, J-48 was the better algorithm with an accuracy of 75.97\%. Results show
that the data gathered from the non-obtrusive sensors can successfully be used
as another input to classification models in order to predict an individual's
affective states during their interaction with a programming tutoring system.
\end{abstract}

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Kevin Bacon}
\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
Georgia Institute of Technology\\
Atlanta, Georgia 30332--0250\\
Email: http://www.kev.org/contact.html}
\and
\IEEEauthorblockN{Homer Simpson}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: homer@thesimpsons.com}
\and
\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
\IEEEauthorblockA{Starfleet Academy\\
San Francisco, California 96678--2391\\
Telephone: (800) 555--1212\\
Fax: (888) 555--1212}}

@@

% make the title area

\maketitle
\begin{abstract} Learning a programming language is a hard thing to do.

\end{abstract}
